---
title: "Modeling and prediction for movies"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### LOAD packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(statsr)
```

### Load data

Make sure your data and R Markdown files are in the same directory. When loaded
your data file will be called `movies`. Delete this note when before you submit 
your work. 

```{r load-data}
#load("movies.Rdata")
```



* * *

## Part 1: Data

This data set deals with the attributes of movies.This set has data about how much audiences and critics like movies as well as numerous other variables about the movies and it includes information from Rotten Tomatoes and IMDB for a random sample of movies.The data set is comprised of 651 randomly sampled movies produced and released before 2016.Each row represents a movies and answer some informational characteristics about them.

**As random sampling was used to collect the data  so we can generalize the data for a bigger population.**

**But we can do a casual inference because there has been no random assisgnment during the colllection of data.**


* * *

## Part 2: Research question

Here the given data is a collection of information and rating both imdb and rotten tomatoes for 651 movies those were released before 2016. From this data set I want to find out a linear regression model that fits for the IMDB ratings for a movie. Here my response variable will be IMDB ratings. I want know about the characteristics that make a movies more likely to get a better rating on IMDB. 
I will be using the existing variables to answer the question without making any new ones.

* * *

## Part 3: Exploratory data analysis

Here as the exploratory data analysis I will see the relationship of variables title genre,studio, critics_score, audience_score, best_pic_nom, best_pic_win, best_actor_win, best_actress, best_dir_win, top200_box, director with response variable imdb_rating.

I did not chose variables relating to the url, catagorical info about actors and DVD release date because these clearly do not seem to have any relation with imdb rating.

Here *I will use the corelation co-efficient to check how strongly a variable is related to imdb rating*. Then *I will check the histogram of each variable to check if their distribuion is nearly normal*. Finally, *I will check their residual plots to check if the variability is conastant*

From the results I will chose my suitable variables for *colinearity testing*.

After this I will chose my secondary variables for modeling.

### Section A: **Linearity Check**
* * *

## Part 4: Modeling

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button above. Make sure that your code is visible in the project you submit. 
Delete this note when before you submit your work.

* * *

## Part 5: Prediction

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button above. Make sure that your code is visible in the project you submit. 
Delete this note when before you submit your work.

* * *

## Part 6: Conclusion

