---
title: "Modeling and prediction for movies"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### LOAD packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(statsr)
library(GGally)
```

### Load data

Make sure your data and R Markdown files are in the same directory. When loaded
your data file will be called `movies`. Delete this note when before you submit 
your work. 

```{r load-data}
load("movies.Rdata")
```


* * *

## Part 1: Data

This data set deals with the attributes of movies.This set has data about how much audiences and critics like movies as well as numerous other variables about the movies and it includes information from Rotten Tomatoes and IMDB for a random sample of movies.The data set is comprised of 651 randomly sampled movies produced and released before 2016.Each row represents a movies and answer some informational characteristics about them.

**As random sampling was used to collect the data  so we can generalize the data for a bigger population.**

**But we can do a casual inference because there has been no random assisgnment during the colllection of data.**


* * *

## Part 2: Research question

Here the given data is a collection of information and rating both imdb and rotten tomatoes for 651 movies those were released before 2016. From this data set I want to find out a linear regression model that fits for the IMDB ratings for a movie. Here my response variable will be IMDB ratings. I want know about the characteristics that make a movies more likely to get a better rating on IMDB. 
I will be using the existing variables to answer the question without making any new ones.

* * *

## Part 3: Exploratory data analysis

Here as the exploratory data analysis I will see the relationship of variables critics_score, audience_score, best_pic_nom, best_pic_win , best_actor_win, best_actress_win, best_dir_win, top200_box, director with response variable imdb_rating.

I did not chose variables relating to the url, catagorical info about actors and DVD release/ theatre release date because these clearly do not seem to have any relation with imdb rating.

Here **I will use linear modeling and their residual plots to determine linearity**. **Then I will use corelation co-efficient for examining any colinear relationship.** 

From the results I will chose my suitable variables for *colinearity testing*.

After this I will chose my secondary variables for modeling.

### Section A: **Linearity Check**

Here I will examine the linear relations of variables genre, critics_score, audience_score,best_pic_nom,best_pic_win, best_actor_win, best_actress_win, best_dir_win, top200_box with imdb_ratings one by one with help of histograme and residual plots.

**(1)** we examine relatios between imdb_ratings and critics_score.
```{r }
 critics_lm <- lm(formula = imdb_rating ~ critics_score, data = movies)

summary(critics_lm)

ggplot(data = critics_lm, aes(sample = .resid)) + stat_qq() + stat_qq_line()

ggplot(data = critics_lm, aes(x = .resid)) +
  geom_histogram() +
  xlab("Residuals")
```
Summary of this linear model shows a high adjused R square. Also the residual distributionn is nearly  noraml around zero. From this we can see linear relation beween this two variables.

**(2)** we examine relatios between imdb_ratings and audience_score
```{r}
audience_lm <- lm(formula = imdb_rating ~ audience_score, data = movies)

summary(audience_lm)

ggplot(data = audience_lm, aes(sample = .resid)) + stat_qq() + stat_qq_line()

ggplot(data = audience_lm, aes(x = .resid)) +
  geom_histogram() +
  xlab("Residuals")
```
Summary of this linear model shows a high adjused R square. BUt the residual distributionn is nearly  noraml around zero (slightly left skewed). From this we can see a weak linear relation beween this two variables.


**(3)** we examine relatios between imdb_ratings and best_pic_nom
```{r}
best_pic_nom_lm <- lm(formula = imdb_rating ~ best_pic_nom, data = movies)

summary(best_pic_nom_lm)

ggplot(data = best_pic_nom_lm, aes(sample = .resid)) + stat_qq() + stat_qq_line()

ggplot(data = best_pic_nom_lm, aes(x = .resid)) +
  geom_histogram() +
  xlab("Residuals")
```
Summary of this linear model shows a low adjused R square. The residual distributionn is nearly  noraml around zero. From this we can see linear relation beween this two variables.


**(4)** we examine relatios between imdb_ratings and best_pic_win
```{r}
best_pic_win_lm <- lm(formula = imdb_rating ~ best_pic_win, data = movies)

summary(best_pic_win_lm)

ggplot(data = best_pic_win_lm, aes(sample = .resid)) + stat_qq() + stat_qq_line()

ggplot(data = best_pic_win_lm, aes(x = .resid)) +
  geom_histogram() +
  xlab("Residuals")
```
Summary of this linear model shows a low adjused R square. BUt the residual distributionn is nearly  noraml around zero. From this we can see linear relation beween this two variables.


**(5)** we examine relatios between imdb_ratings and best_actor_win
```{r}
best_actor_win_lm <- lm(formula = imdb_rating ~ best_actor_win, data = movies)

summary(best_actor_win_lm)

ggplot(data = best_actor_win_lm, aes(sample = .resid)) + stat_qq() + stat_qq_line()

ggplot(data = best_actor_win_lm, aes(x = .resid)) +
  geom_histogram() +
  xlab("Residuals")
```
Summary of this linear model shows a low adjused R square. The residual distributionn is nearly  noraml around zero but it lacks constant variance. From this we can see a very weak linear relation beween this two variables.


**(6)** we examine relatios between imdb_ratings and best_actress_win
```{r}
best_actress_win_lm <- lm(formula = imdb_rating ~ best_actress_win, data = movies)

summary(best_actress_win_lm)

ggplot(data = best_actress_win_lm, aes(sample = .resid)) + stat_qq() + stat_qq_line()

ggplot(data = best_actress_win_lm, aes(x = .resid)) +
  geom_histogram() +
  xlab("Residuals")
```
Summary of this linear model shows a low adjused R square. The residual distributionn is nearly  noraml around zero but it lacks constant variance. From this we can see a very weak linear relation beween this two variables.

**(7)** we examine relatios between imdb_ratings and best_dir_win.
```{r}
best_dir_win_lm <- lm(formula = imdb_rating ~ best_dir_win, data = movies)

summary(best_dir_win_lm)

ggplot(data = best_dir_win_lm, aes(sample = .resid)) + stat_qq() + stat_qq_line()

ggplot(data = best_dir_win_lm, aes(x = .resid)) +
  geom_histogram() +
  xlab("Residuals")
```
Summary of this linear model shows a low adjused R square. The residual distributionn is nearly  noraml around zero but it lacks constant variance. From this we can see a very weak linear relation beween this two variables.

**(8)** we examine relatios between imdb_ratings and top200_box.
```{r}
top200_box_lm <- lm(formula = imdb_rating ~ top200_box, data = movies)

summary(top200_box_lm)

ggplot(data = top200_box_lm, aes(sample = .resid)) + stat_qq() + stat_qq_line()

ggplot(data = top200_box_lm, aes(x = .resid)) +
  geom_histogram() +
  xlab("Residuals")
```
Summary of this linear model shows a low adjused R square. The residual distributionn is nearly  noraml around zero but it lacks constant variance. From this we can see a  weak linear relation beween this two variables.

**(9)** we examine relatios between imdb_ratings and director.
```{r}
director_lm <- lm(formula = imdb_rating ~ director, data = movies)

summary(director_lm)

ggplot(data = director_lm, aes(sample = .resid)) + stat_qq() + stat_qq_line()

ggplot(data = director_lm, aes(x = .resid)) +
  geom_histogram() +
  xlab("Residuals")
```
Summary of this linear model shows a high adjused R square. Also the residual distributionn is nearly  noraml around zero. From this we can see linear relation beween this two variables.


**(10)** we examine relatios between imdb_ratings and genre
```{r}
genre_lm <- lm(formula = imdb_rating ~ genre, data = movies)

summary(genre_lm)

ggplot(data = genre_lm, aes(sample = .resid)) + stat_qq() + stat_qq_line()

ggplot(data = genre_lm, aes(x = .resid)) +
  geom_histogram() +
  xlab("Residuals")
```
Summary of this linear model shows a high adjused R square. Also the residual distributionn is nearly  noraml around zero. From this we can see linear relation beween this two variables.

**From our above exloration we see director, audience_score, critics_score, best_pic_win variables have a linear realtion with imdb_ratings.**


### Section B: **Co-linearity Check**


There is a co-linearity between audience_score and critics_score.
```{r}
cor(movies$audience_score,movies$critics_score)
```
So we can not choose both. **Here I will take audience_score because it serves a better model.**

* * *
## Part 4: Modeling
Now I will use **backward elemination** on adjusted R squares to chose my model.

I have selected genre, director, audience_score, critics_score, best_pic_win variables for calculating model *parsimony*.

At first we will check adjusted R squares including all variales.

```{r}
m0 <- lm(formula = imdb_rating ~ director + genre + audience_score + best_pic_win, data = movies) 

summary(m0)$adj.r.squared
```
Now I will eleminate each variable and check the adjusted r square value for that model. 

**model 1: **(eliminating genre)
```{r}
m1 <- lm(formula = imdb_rating ~ director + audience_score + best_pic_win, data = movies) 

summary(m0)$adj.r.squared
```

**model 2: **(eliminating director)

```{r}
m2 <- lm(formula = imdb_rating ~ genre + audience_score + best_pic_win, data = movies) 

summary(m0)$adj.r.squared
```
**model 3: **(eliminating audience_score)

```{r}
m3 <- lm(formula = imdb_rating ~ genre + director + best_pic_win, data = movies) 

summary(m0)$adj.r.squared
```

**model 4: **(eliminating best_pic_win)
```{r}
m4 <- lm(formula = imdb_rating ~ director + audience_score + genre, data = movies) 

summary(m0)$adj.r.squared
```

At this point of our analysis model 1 has the most adjusted r square value. Now we will eliminate each variable from model 1 once and check adjusted r square.

**model 5: **(eliminating director from model 1)
```{r}
m5 <- lm(formula = imdb_rating ~  audience_score + genre, data = movies) 

summary(m0)$adj.r.squared
```


**model 6: **(eliminating audience_score from model 1)
```{r}
m5 <- lm(formula = imdb_rating ~  director + genre, data = movies) 

summary(m0)$adj.r.squared
```

**model 7: **(eliminating genre from model 1)
```{r}
m5 <- lm(formula = imdb_rating ~  audience_score + director, data = movies) 

summary(m0)$adj.r.squared
```

Here we can see adjusted r square does not increase if we eliminate any variable from model 1.

Thus **model 1** is my final selention.
* * *

## Part 5: Prediction

I Will use my linear model described above to predict the imdb ratings for the movie "Dunkirk". 
For this prediction I will need the name of the director, audience score from rotten tomaotes and genre.
This is an action film directed by Christoppher Nolan. my pridiction for this film.

```{r}
new_movie <- data.frame(director = "Christopher Nolan", audience_score = 88, best_pic_win = "no")

predict(m1, new_movie, interval = "prediction", level = 0.95)
```
 From this we can say that we are 95% confident about the imdb ratings for the movie "Dunkirk" is **expected** to be in between 7.488698 and 9.123914. 
 
My Multiple linear model shows the rating is *expected* to be 8.306306.

The actual imdb rating for this movie is 7.9. My findings is prettty close to the actual rating.

* * *
## Part 6: Conclusion

I tried every potential variables that can be a possible predictor of imdb rating. I explored their relationship with the ratings with the help linear modeling and plots. I also checked the colinearity between my most potential variables.

After that I used backward elimination to find out the best model for my question.

My model predicts the imdb rating for any movie almost 95% accurately.

From my study I learned important three charecteristics for any movie to have notable impact on its imdb ratings. As my result is not 100% accurate, there is obviously some shortcoming. This shortcoming can be overcome if there were more variables/Info in the data that were related to imdb ratings. Then we can have a more precise model with variables that make a moviemore likely to get a better rating on IMDB.



##Thank you.